Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification

### 2021-09-17 article.tex
doi
fin

\documentclass[sigplan,10pt]{acmart}
% \settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[underline=true,rounded corners=false]{pgf-umlsd} % for UML sequence diagrams
\usepackage[square]{syntax} % for BNF grammar
  \setlength{\grammarparsep}{1pt}
  \setlength{\grammarindent}{2em}
\usepackage{array} % complex structure of TABULAR-s
\usepackage{paralist} % for inline itemized lists env{inparaenum}
\usepackage{natbib} % for customization of bibliography headers
\usepackage{ffcode}
\usepackage{tikz}
  \usetikzlibrary{shapes,arrows,shadows}
  \usetikzlibrary{decorations.pathmorphing}
  \usetikzlibrary{positioning,fit}
  \usetikzlibrary{calc}

@@

\title{Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification}
\author{Yegor Bugayenko}{}{}
\email{yegor256@gmail.com}
\affiliation{\institution{}\city{Moscow}\country{Russia}}
\setcopyright{acmcopyright}
\copyrightyear{2021}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011074.10011075.10011076</concept_id>
<concept_desc>Software and its engineering~Requirements analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Software and its engineering~Requirements analysis}
\acmConference[BCNC 2021]
  {1st ACM SIGPLAN International Workshop on Beyond Code: No Code}
  {October 17, 2021}
  {Chicago, IL, US}
\keywords{Requirements, Natural Language Processing}

@@

Third, developing requirements specification with the language requires RE
engineers to understand key principles of ``object thinking''~\citep{west04},
like ``everything is an object'' and ``objects expose behavior, not state.''
Initial training was required in two projects.

>>>>

\documentclass[sigplan,10pt,screen]{acmart}
% \settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[underline=true,rounded corners=false]{pgf-umlsd} % for UML sequence diagrams
\usepackage[square]{syntax} % for BNF grammar
  \setlength{\grammarparsep}{1pt}
  \setlength{\grammarindent}{2em}
\usepackage{array} % complex structure of TABULAR-s
\usepackage{paralist} % for inline itemized lists env{inparaenum}
\usepackage{natbib} % for customization of bibliography headers
\usepackage{ffcode}
\usepackage{flushend}
\usepackage{tikz}
  \usetikzlibrary{shapes,arrows,shadows}
  \usetikzlibrary{decorations.pathmorphing}
  \usetikzlibrary{positioning,fit}
  \usetikzlibrary{calc}

@@

\title{Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification}
\author{Yegor Bugayenko}
\orcid{0000-0001-6370-0678}
\email{yegor256@gmail.com}
\affiliation{\city{Moscow}\country{Russia}}

\setcopyright{acmcopyright}
\acmPrice{15.00}
\acmDOI{10.1145/3486949.3486963}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{splashws21bcncmain-p41-p}
\acmISBN{978-1-4503-9125-2/21/10}
\acmConference[BCNC '21]{Proceedings of the 1st ACM SIGPLAN International Workshop on Beyond Code: No Code}{October 17, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 1st ACM SIGPLAN International Workshop on Beyond Code: No Code (BCNC '21), October 17, 2021, Chicago, IL, USA}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011074.10011075.10011076</concept_id>
<concept_desc>Software and its engineering~Requirements analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Software and its engineering~Requirements analysis}
\keywords{Requirements, Natural Language Processing}

@@

Third, developing requirements specification with the language requires RE
engineers to understand key principles of ``object thinking''~\citep{west04,eo1},
like ``everything is an object'' and ``objects expose behavior, not state.''
Initial training was required in two projects.
